\documentclass[main.tex]{subfiles}

\begin{document}

\section{Conjectural lifting properties of left Kan extensions}
\label{sec:con_extensions}

We provide a conjectural answer to the following question. Let $f\colon X \to Y'$ be a map of Kan complexes, and let $\mathcal{F}\colon X \to \category{C}$ be a functor, where $\category{C}$ is cocomplete. What universal property does the $\infty$-Kan extension $f_{!}\mathcal{F}\colon Y \to \category{C}$ satisfy? More generally, we would like an answer to this question where $X$ and $Y$ are $\infty$-categories rather than just spaces.

A left Kan extension should be modelled by a 2-simplex in $\ICCat$
\begin{equation*}
  \label{eq:left_kan_ext}
  \begin{tikzcd}
    X
    \arrow[rr, "\mathcal{F}", ""{below, name=M}]
    \arrow[dr, swap, "f"]
    && \category{C}
    \\
    & Y
    \arrow[ur, swap, "f_{!}\mathcal{F}"]
    \arrow[from=M, Rightarrow, "\eta"]
  \end{tikzcd},
\end{equation*}
where $\eta$ is the unit map. In analogy to the 1-categorical case, it is logical to assume that such $2$-simplices would enjoy certain pleasant lifting properties. Here is the property we need to hold in order to make our construction work out.

This definition is terribly-phrased, but it'll get the job done.
\begin{definition}
  \label{def:left_kan}
  A 2-simplex $\sigma\colon \Delta^{2}_{\flat} \to \ICCat$ is \defn{left Kan} if either of the following equivalent hold.
  \begin{enumerate}
    \item For all
      \begin{equation*}
        \tau\colon ( \Lambda^{3}_{0} )_{\flat} \to \ICCat
      \end{equation*}
      such that 
      \begin{itemize}
        \item $d_{2}\tau = \sigma$, and

        \item the image of each vertex $\Delta^{\{i\}}$ under $\tau$ is a small Kan complex\footnote{We don't need to assume Kan complex here, just $\infty$-category, but I don't wanna make my life any harder than it needs to be.} for $0 \leq i < 3$, and

        \item the image of the vertex $\Delta^{\{3\}}$ under $\tau$ is a cocomplete $\infty$-category,
      \end{itemize}
      The space
      \begin{equation*}
        \left( \Map(\Delta^{3}_{\flat}, \ICCat) \times_{\Map((\Lambda^{3}_{0})_{\flat}, \ICCat)} \{\tau\} \right)^{\simeq}
      \end{equation*}
      of fillings of $\tau$ to a full 3-simplex is contractible.

    \item For each $n \geq 3$ and any
      \begin{equation*}
        \tau\colon (\Lambda^{n}_{0})_{\flat} \to \ICat
      \end{equation*}
      such that 
      \begin{itemize}
        \item $\tau|_{\Delta^{\{0,1,n\}}} = \sigma$,

        \item the image of each vertex $\Delta^{\{i\}}$ under $\tau$ is a small Kan complex for $0 \leq i < 3$, and

        \item the image of the vertex $\Delta^{\{3\}}$ under $\tau$ is a cocomplete $\infty$-category,
      \end{itemize}
      a filling of $\tau$ to a full $n$-simplex exists.
  \end{enumerate}

  \begin{note}
    It's not yet clear to me which of these definitions will be easier to use. They really are equivalent because of the following fact: for any categorical fibration $p\colon \category{C} \to \category{D}$, a morphism $f$ in $\category{C}$ is $p$-cocartesian if either of the following equivalent holds:
    \begin{itemize}
      \item For all $n \geq 2$, the space of solutions to the lifting problem
        \begin{equation*}
          \begin{tikzcd}
            \Delta^{\{0, 1\}}
            \arrow[dr, "f"]
            \arrow[d]
            \\
            \Lambda^{n}_{0}
            \arrow[r]
            \arrow[d]
            & \category{C}
            \arrow[d]
            \\
            \Delta^{n}
            \arrow[r]
            \arrow[ur, dashed]
            & \category{D}
          \end{tikzcd}
        \end{equation*}
        is nonempty.

      \item The space of solutions to the lifting problem
        \begin{equation*}
          \begin{tikzcd}
            \Delta^{\{0, 1\}}
            \arrow[rd, "f"]
            \arrow[d]
            \\
            \Lambda^{2}_{0}
            \arrow[r]
            \arrow[d]
            & \category{C}
            \arrow[d]
            \\
            \Delta^{2}
            \arrow[r]
            \arrow[ur, dashed]
            & \category{D}
          \end{tikzcd}
        \end{equation*}
        is contractible.
    \end{itemize}
  \end{note}


  %Or: if for all $n \geq 3$, we can find a lift
  %\begin{equation*}
  %  \begin{tikzcd}
  %    \Delta^{\{0,1,n\}}
  %    \arrow[d, hook]
  %    \arrow[dr, "\sigma"]
  %    \\
  %    \Lambda^{n}_{0}
  %    \arrow[r]
  %    \arrow[d, hook]
  %    & \ICCat
  %    \\
  %    \Delta^{n}
  %    \arrow[ur, dashed]
  %  \end{tikzcd}
  %\end{equation*}
\end{definition}

\begin{definition}
  \label{def:pointwise_left_kan}
  A 2-simplex $\sigma\colon \Delta^{2}_{\flat} \to \ICCat$ is \defn{pointwise left Kan} if it is of the form
  \begin{equation*}
    \begin{tikzcd}
      X
      \arrow[rr, "\mathcal{F}", ""{below, name=M}]
      \arrow[dr, swap, "f"]
      && \category{C}
      \\
      & Y
      \arrow[ur, swap, "f_{!}\mathcal{F}"]
      \arrow[from=M, Rightarrow, "\eta"]
    \end{tikzcd},
  \end{equation*}
  where $X$ and $Y$ are small Kan complexes, $\category{C}$ is a cocomplete $\infty$-category, $f_{!}F$ is a left Kan extension of $F$ along $f$, and $\eta$ is a unit map.
\end{definition}

\begin{proposition}
  Let $\tau\colon \Delta^{2}_{\flat} \to \ICCat$ be pointwise left Kan. Then it is left Kan.
\end{proposition}
\begin{proof}
  Let $(\Lambda^{3}_{0})_{\flat} \to \ICat$ be a map satisfying the conditions of \hyperref[def:pointwise_left_kan]{Definition~\ref*{def:pointwise_left_kan}}, corresponding to a horn
\end{proof}


\end{document}
