\documentclass[a4paper,12pt]{scrartcl}

\usepackage{mystyle}
\usepackage{subfiles}

%bibliography location
%\addbibresource{/home/angus/latex/masters_notes/sources.bib}

\title{Monoidal push-pull for local systems}
\author{Angus Rush}

\begin{document}

\maketitle 
\tableofcontents

\section{Introduction}
\label{sec:introduction}

This is not meant to be a finished document, as there are still some gaps (listed below). It follows very closely the structure of my thesis, and I use a lot of results from there. It will not yet make sense on its own, and you may need to refer to my thesis to find the definitions of certain terms.

The gaps include:

\begin{itemize}
  \item I'm using some things that don't exist yet, or at least which I haven't been able to find anywhere:
    \begin{itemize}
      \item An extrinsic description of left Kan extensions in $\ICCat$. That is, if I know that a morphism in $\ICCat$ is a left Kan extension, can I use this to solve lifting problems in $\ICCat$? A more concrete description of the universal property that I need is in section 3.

      \item The easy overcategory colimit formula for non-inclusions: In Ambidexterity, Lurie uses that the colimit formula for left Kan extensions can be given in terms of overcategories even along non-inclusions. I'm perfectly willing to believe this, but I haven't been able to find a reference.

      \item A functorial twisted arrow category.
    \end{itemize}

  \item In showing that certain maps in $\LS(\category{C})$ are left Kan extensions, I still need to show that the natural transformations involved are the unit maps.

  \item I'm ignoring size issues.
\end{itemize}

%\subfile{background.tex}
\subfile{new_barwick.tex}
\subfile{con_extensions.tex}
\subfile{non_monoidal.tex}
\subfile{base_fibrations.tex}
%\subfile{don_quixote.tex}

%\printbibliography

\end{document}

